Using an SMT engine to generate Symbolic Automata

### 2019-03-08 2017-Xudong-SMT/ActaInformatica.tex
tableau resultats

\begin{table}[t]\caption{\label{table:BIPalgebra}\leftline{Algebra
      Presentation: predefined Sorts and Operators}}
	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Sort & Constructors & Auxiliary Operators
                \\\specialrule{0em}{1pt}{1pt}
		\hline\specialrule{0em}{3pt}{3pt}
		Bool    			&
                $\texttt{true},\ \texttt{false}$&
                $\land,\ \lor,\ \neg,\ \implies,\ =,\ \ne$
                \\\specialrule{0em}{1pt}{1pt} 
                %               		Action 			&  $\texttt{Synchro},\ \texttt{FUN\_Action\_Bool}$ &
                Action 			&  $\texttt{Synchro},\ \texttt{FUN}$ &
                \\\specialrule{0em}{1pt}{1pt}
		Int 				&
                ${0, \{i, -i\}_{i \in \texttt{Nat}}}$  &
                $- \texttt{(unary)},\ +,\ -
                \texttt{(binary)},\ \times,\ \div \text{ \etc}$
%                \\\specialrule{0em}{1pt}{1pt}
%                \textsl{for any sort} & & $=,\ \ne$
		\\\hline\specialrule{0em}{1pt}{1pt}
\multicolumn{3}{l}{\sl Extension for the BIP use-case of Fig.~\ref{schema:ArchFailure:pNet}}
		\\\hline\specialrule{0em}{1pt}{1pt}
                Action & \multicolumn{2}{l} \texttt{FUN\_Action\_Bool}, \texttt{}fail, resume, timeout, reset, start, tick, ask 
		\\\hline
	\end{tabular}
\end{table}

@@

Algorithm~\ref{alg3} implement this new stategy: ...

@@

>>>>

\begin{table}[t]\caption{\label{table:BIPalgebra}\leftline{Algebra
      Presentation: predefined Sorts and Operators}}
	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Sort & Constructors & Auxiliary Operators
                \\\specialrule{0em}{1pt}{1pt}
		\hline\specialrule{0em}{3pt}{3pt}
		Bool    			&
                $\texttt{true},\ \texttt{false}$&
                $\land,\ \lor,\ \neg,\ \implies,\ =,\ \ne$
                \\\specialrule{0em}{1pt}{1pt} 
                %               		Action 			&  $\texttt{Synchro},\ \texttt{FUN\_Action\_Bool}$ &
                Action 			&  $\texttt{Synchro},\ \texttt{FUN}$ &
                \\\specialrule{0em}{1pt}{1pt}
		Int 				&
                ${0, \{i, -i\}_{i \in \texttt{Nat}}}$  &
                $- \texttt{(unary)},\ +,\ -
                \texttt{(binary)},\ \times,\ \div \text{ \etc}$
%                \\\specialrule{0em}{1pt}{1pt}
%                \textsl{for any sort} & & $=,\ \ne$
		\\\hline\specialrule{0em}{1pt}{1pt}
\multicolumn{3}{l}{\sl Extension for the BIP use-case of Fig.~\ref{schema:ArchFailure:pNet}}
		\\\hline\specialrule{0em}{1pt}{1pt}
                Action & \multicolumn{2}{l} \texttt{FUN\_Action\_Bool}, \texttt{}fail, resume, timeout, reset, start, tick, ask 
		\\\hline
	\end{tabular}

\end{table}

@@

Algorithm~\ref{alg3} implement this new stategy: \TODO{Explain
  significant detials}

@@

\subsection{Benefits from the Smart algorithm}

	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Use-case & Brute force & Smart algorithm
                \\\specialrule{0em}{1pt}{1pt}
		\hline\specialrule{0em}{3pt}{3pt}
		Enable operator   			&
                5 SAT OTs           &
                5 SAT OTs
                \\\specialrule{0em}{1pt}{1pt}

                ``(P>Q)>R'' &
                55 UNSAT           &
                42 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                376 ms 				&
                344 ms  
		\\\hline\specialrule{0em}{3pt}{3pt}
		SimpleProt    			&
                7 SAT OTs           &
                7 SAT OTs
                \\\specialrule{0em}{1pt}{1pt}

                (no holes)&
                260 UNSAT           &
                57 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                1536 ms 				&
                359 ms  
%                \\\specialrule{0em}{1pt}{1pt}
%                \textsl{for any sort} & & $=,\ \ne$
		\\\hline\specialrule{0em}{1pt}{1pt}
		SimpleProt    			&
                19 SAT OTs           &
                19 SAT OTs
                \\\specialrule{0em}{1pt}{1pt}

                (with 2 client holes)&
                836 UNSAT           &
                185 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                2496 ms 				&
                844 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer    			&
                12 SAT OTs           &
                12 SAT OTs
                \\\specialrule{0em}{1pt}{1pt}

                (no Max Progress)&
                1253 UNSAT           &
                812 UNSAT
                \\\specialrule{0em}{1pt}{1pt}
		&
                1253 ms 				&
                812 ms

		\\\hline
	\end{tabular}
